Semantic Textual Similarity using deep learning

### 2017-06-05 paper/main.tex
Added baseline descriptions

\name{Bruno Gavranovic, Neven Miculinic, Stipan Mikulic}

@@

%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=\columnwidth]{sen_len_no_stop.png}
%\caption{Sentence lengths without stopwords}
%\label{fig:lstm_2nd_layer}
%\end{center}
%\end{figure}
%
%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=\columnwidth]{sen_len_with_stop.png}
%\caption{Sentence lengths with stopwords}
%\label{fig:lstm_2nd_layer}
%\end{center}
%\end{figure}
%
%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=\columnwidth]{tokens_no_stop.png}
%\caption{Number of tokens without stopwords}
%\label{fig:lstm_2nd_layer}
%\end{center}
%\end{figure}
%
%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=\columnwidth]{tokens_with_stop.png}
%\caption{Number of tokens with stopwords}
%\label{fig:lstm_2nd_layer}
%\end{center}
%\end{figure}

\newpage
\subsection{SVM}

>>>>

\name{Bruno Gavranović, Neven Miculinić, Stipan Mikulić}

@@

%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=\columnwidth]{sen_len_no_stop.png}
%\caption{Sentence lengths without stopwords}
%\label{fig:lstm_2nd_layer}
%\end{center}
%\end{figure}
%
%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=\columnwidth]{sen_len_with_stop.png}
%\caption{Sentence lengths with stopwords}
%\label{fig:lstm_2nd_layer}
%\end{center}
%\end{figure}
%
%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=\columnwidth]{tokens_no_stop.png}
%\caption{Number of tokens without stopwords}
%\label{fig:lstm_2nd_layer}
%\end{center}
%\end{figure}
%
%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=\columnwidth]{tokens_with_stop.png}
%\caption{Number of tokens with stopwords}
%\label{fig:lstm_2nd_layer}
%\end{center}
%\end{figure}
\subsection{Baseline models}

To get an idea of how well our models perform, we used two baseline models.
Neither of them is a machine learning model; in other words, they do not learn from data, but are rather simple statistics measures.

\subsubsection{Jaccard similarity baseline}

One of the simplest approaches to measuring semantic similarity is the Jaccard rindex.
It is a statistic used for comparing similarity and diversity of finite sets.
Let $J(S_1, S_2)$ represent the Jaccard index between two sentences $S_1$ and $S_2$.
The similariy between sentences is defined as:
\begin{equation}
	\label{eq:jaccard}
	J(S_1, S_2) = \frac{|S_1 \cap S_2|}{|S_1 \cup S_2|},
\end{equation}

where the elements of $S_1$ and $S_2$ are their words, in lowercase.

\subsubsection{Cosine similarity}

Unlike in the encodings of images, necessary information to decode the data is \textit{not} stored in the encodings of words.
Natural language is encoded in arbitrary sequences of symbols and provides no useful information to the model regarding the relationships that may exist between various concepts.
One method that is effectively captures the semantic meaning behind the various concepts are the word embeddings.

Simple approach to extending the word embedding system to a sentence is simply performing some aggregation operation on each of the embeddings.
We used the summation function aggregation on the words of the sentence, after removing stopwords.
Stopwords list is used from the NLTK library.
Word embedding used is the English version of the FastText word embeddings \citep{joulin2016fasttext}.

\subsection{SVM}
